\cvsection{Experience}
\begin{cventries}
  \cventry
    {Full Stack Developer}
    {New York Office, IIT Kanpur(Prof. Manindra Agrawal)}
    {Kanpur, India}
    {Jul. 2017 - Present}
    {
      \begin{cvitems}
        \item {Working on the frontend and the backend of a fully scalable web application, to improve it}
        \item {The frontend is based on Angular and typescript, while the backend involves technologies like Scala with Akka, Slick, everything collaborated through Phabricator.}
        \item {Currently trying to add database migrations for the web application.}
      \end{cvitems}
    }
    \cventry
    {Senior Executive, Backend}
    {Techkriti, Web}
    {IIT Kanpur}
    {Jul. 2017 - Present}
    {
      \begin{cvitems}
        \item {Techkriti is the annual techfest of IIT Kanpur.}
        \item {I am working on the backend of the fest's website}
        \item {In charge of reducing code renundancy and scaling the web application.}
        \item {Technologies used include Docker, Node.js and MongoDB}
      \end{cvitems} 
    }    
 \cventry
    {Backend Developer(Summer Internship)}
    {New York Office, IIT Kanpur(Prof. Manindra Agrawal)}
    {Kanpur, India}
    {Summer'17}
    {
      \begin{cvitems}
        \item {Worked on the search API in the backend based on ElasticSearch.}
        \item {Used Scala with Akka for backend development with Phabricator for collaboration.}
        \item {Used slick as typesafe query and access library using FRM.}
      \end{cvitems}
    }
  \cventry
    {Realtime Chat application - LetsChat}
    {Code.Fun.Do}
    {IIT Kanpur}
    {January,2017}
    {
      \begin{cvitems}
        \item {Made a realtime android chat application}
        \item {The app was made on Android Studio with frontend in XML and Firebase which is a realtime database, on the backend.}
        \item {The app was successfully submitted}
      \end{cvitems}
    }
  \cventry
\end{cventries}
